
\documentclass{dcthesis}

\usepackage[export]{adjustbox} % in preambl
\usepackage[normalem]{ulem}
\usepackage{circuitikz}
\usepackage{longtable}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{amssymb,amsthm,amsmath,amstext}
\usepackage{mathrsfs}  % allows nice script font for sheaves
% \usepackage{bm}        % allows bold italic letters in math mode
% \usepackage{mathtools} % allows more extendible arrows
\usepackage{stmaryrd}  % additional nice fonts
\usepackage{mathtools}
\usepackage{geometry}
\usepackage{xy}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{lipsum}
\usepackage{caption}
\usepackage{circuitikz}
\usepackage{tikz-cd}
\usepackage{bbm}
\usepackage{hyperref}
\usepackage{enumerate}% http://ctan.org/pkg/enumerate
\usepackage{tikz}
\usepackage{tikz-cd}
\usepackage{dirtytalk}
\usetikzlibrary{calc}
\usetikzlibrary{positioning, shapes, shapes.geometric, fit}
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  filecolor=magenta,
  urlcolor=cyan,
  pdftitle={Overleaf Example},
  pdfpagemode=FullScreen,
}

\makeatletter
\renewcommand{\@chapapp}{}% Not necessary...
\newenvironment{chapquote}[2][2em]
{\setlength{\@tempdima}{#1}%
  \def\chapquote@author{#2}%
  \parshape 1 \@tempdima \dimexpr\textwidth-2\@tempdima\relax%
\itshape}
{\par\normalfont\hfill--\ \chapquote@author\hspace*{\@tempdima}\par\bigskip}
\makeatother

\DeclareCaptionFormat{algor}{%
  \hrulefill\par\offinterlineskip\vskip1pt%
\textbf{#1#2}#3\offinterlineskip\hrulefill}
\DeclareCaptionStyle{algori}{singlelinecheck=off,format=algor,labelsep=space}
\captionsetup[algorithm]{style=algori}

%This version of the thesis template has been updated for the
% February 2017 thesis guidelines provided by the School of Graduate
% and Advanced Studies by David Freund and Daryl DeFord.

%  Some good options are draft and singlespacing, for drafts, and *final*,
%for the final cut, and noheadings, for a printout without headings.
%You can also use the copyright option to add a copyright.  Note:
%final will enforce a bunch of different options, like oneside, 12pt
%and doublespacing, as well as make the margins correct.   Draft, has
%larger margins and is appropriate for twosided printing.

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%    IMPORTANT     %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  Because dvips doesn't know/care about the page size of the dvi file
%  its working on, and because its so important that the margins of
%  your thesis are correct you have to make sure that you are using
%  the command dvi -t letter *thesisnamehere*
%
%  If you are using a terminal this is straightforward, but if you are
%  using a tex editing program it make take a little bit of searching
%  before you figure out how to make this work.
%
%  Alternatively, you might consider compiling using pdflatex, which
%  compiles straight to a PDF and doesn't have this problem.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Additional Packages (add as desired)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsmath,amssymb,amsthm}

%\usepackage{mkindex} %Uncomment if you would like to have an index.
% Compiling with an index takes more work than compiling without one.
% You will have to look up how to use the index package.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Formatting
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Change or add to as desired.
%  These two commands make the first enumerations look like (a)
%  And the second level like (i).
\renewcommand{\labelenumi}{(\alph{enumi})}
\renewcommand{\labelenumii}{(\roman{enumii})}
%  These commands make the section headings Boldface and not all
%  caps. It also removes the chapter numbers
\renewcommand{\chaptermark}[1]{\markboth{{\sc #1}}{{\sc #1}}}
\renewcommand{\sectionmark}[1]{\markright{{\sc \thesection\ #1}}}
%  These commands have lowercase headings with chapter numbers.
%\renewcommand{\chaptermark}[1]{markboth{#1}{}}
%\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Theorem Declarations
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% A basic set of theorem declarations.  Add or remove as desired.
\newtheorem{prop}{Proposition}[chapter]
\newtheorem{theorem}[prop]{Theorem}
\newtheorem{lemma}[prop]{Lemma}
\newtheorem{corr}[prop]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[prop]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[prop]{Remark}
\newtheorem{example}[prop]{Example}
\newcommand\dunderline[3][-1pt]{{%
    \sbox0{#3}%
\ooalign{\copy0\cr\rule[\dimexpr#1-#2\relax]{\wd0}{#2}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Indicies
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%This is for an index.  More work is neede for a notation index
%\makeindex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Macros
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Add your math macros here

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title Page Information
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Your personal info goes here!
\title{Action This Day}
\subtitle{The Mathematics and Machinations that Bested the German Enigma}
\author{Jonah Weinbaum}
\date{December 2021}
\degree{Masters of Science}
\field{Computer Science}
\committee{Christophe Hauser}{Sergey Bratus}{Sean Smith}{Asher
Auel}{Peter Winkler}
% \committee[F. Jon Kull, Ph.D.]
\school{Guarini School of Graduate and Advanced Studies}{Dartmouth
College}{Hanover, New Hampshire}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Front end of thesis
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\frontmatter

\newgeometry{left=1.5in,top=1in,bottom=1in,right=1in}
\maketitle
\restoregeometry

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Table of Contents
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\tableofcontents

%Add a list of tables
%\listoftables

%Add a list of figures
%\listoffigures

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Main Portion of Thesis
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%
%%  YOUR THESIS HERE!  %%
%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter*{Abstract}
\addcontentsline{toc}{section}{Abstract}

\chapter*{Aims of Thesis}
\addcontentsline{toc}{section}{Aims of Thesis}
It should be made clear that I am not a historian. As such, this
thesis does not aim to be a perfect retelling of historical
narrative; rather, this thesis aims to convey a chronological
progression of cryptographic attacks on Enigma, culminating in the
creation of the Turing-Welchman Bombe, which is the central focus of
this paper. The paper is structured to gradually build the reader's
understanding of the various flaws in the Enigma machine,
illustrating how and why the Bombe came to take the form that it did.
Historical details are included to advance the mathematical narrative
and are, to the best of my ability, confirmed to be historically accurate.
\\\\The first three chapters of this thesis serve as an expository
resource aimed at mathematically inclined readers seeking depth and
rigor regarding cryptographic attacks on Enigma. The final chapter
presents a novel contribution. It critically examines the
mathematical model by which the Bombe's efficacy was described by
Turing and presents an alternative model that better aligns with the
ground-truth operation of the Bombe.

\chapter*{Requisite Background}
\addcontentsline{toc}{section}{Requisite Background}
The subject matter of this paper concerns both the mathematical and
mechanical means by which the Enigma encryption scheme was broken over time.
\\\\With respect to mathematical background, the reader is expected
to have an introductory knowledge of abstract algebra, in particular
a solid grasp of permutation theory. Further, many topics will delve
into probabilistic and combinatoric analysis of language frequency,
keyspaces, and the effectiveness of various methods. For this reason
the reader is expected to have a comfortable understanding of
introductory combinatorics and Bayesian statistics.
\\\\With respect to mechanical background, the reader requires very
limited knowledge of components such as transistors and relays.
Circuit diagrams will be used sparingly or will be abstracted such as
to reduce the need of an electrical engineering background.

\chapter*{Introduction}
\addcontentsline{toc}{section}{Introduction}
While the allied armies fought tooth and nail, in trenches and tanks,
for the fate of the world, another army was amassed in the small
radio factory of Bletchley Park. Mathematicians, engineers,
linguists, and chess players, armed with paper and pencil, wire and
punch-cards, took up their own battle.
\\\\Hitler's best-kept secrets lay hidden behind a math problem. What
follows is the story of some of history's greatest minds and their
work to solve that problem. It is a story of secrecy and spies;
ingenious perspectives, laborious work, and machines built to think
faster than any human ever had.
\\\\At the center of this story is the Enigma machine, a feat of
cryptography so vast in its possible arrangements that it was thought
unbreakable. Breaking it required more than mathematical trickery; it
required coordination, luck, and a cryptographic intelligence team
the likes of which the world had never seen. Winston Churchill saw
this math problem for what it was: the key to saving millions of
lives. Understanding the project's urgency, he issued a memo
demanding that the utmost attention and resources be given to the
Bletchley team. Churchill tagged this memo with a red stamp reserved
for matters of the highest priority. It read:
\begin{center}
  \textbf{Action This Day}
\end{center}
\mainmatter
\include{the_enigma}
\include{polish_bomba}
\include{uk_bombe}
\include{stops}

%\appendix
%\include{appendixA}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Backend of thesis (references and the like)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \backmatter

%Add your bibliography filename and uncomment these lines
% \bibliographystyle{amsplain}
% \addcontentsline{toc}{chapter}{References}
% \bibliography{citations}
% \markboth{{\sffamily\sc Bibliography}}{}

%Uncomment if you want an index
%\printindex

\end{document}
